Detection and replication of epistasis influencing transcription in humans

### 2013-06-25 docs/manuscript/nature_letter.tex
updates: manuscript close to completion
images updated for
- 3d plots
- circle plots
- genomic features

organised scripts more sensibly

answered most comments from peter and grant on manuscript and methods

just need to calculate variances for replication datasets now

\documentclass{article}
\usepackage[superscript,biblabel]{cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{authblk}

@@

\title{Detection and replication of epistasis influencing transcription in humans}
\date{}
\author[1,2,*]{Gibran Hemani}
\author[1,2]{Konstantin Shakhbazov}
\author[3]{Harm-Jan Westra}
\author[4]{Anjali K Henders}
\author[1,2]{Allan F. McRae}
\author[5]{Andres Metspalu}
\author[6]{Greg Gibson}
\author[4]{Nick G Martin}
\author[5,7,8]{Tonu Esko}
\author[3]{Lude Franke}
\author[4]{Grant W Montgomery}
\author[1,2]{Peter M Visscher}
\author[1,2]{Joseph E Powell}

\affil[1]{University of Queensland Diamantina Institute, University of Queensland, Princess Alexandra Hospital, Brisbane, Queensland, Australia}

\affil[2]{The University of Queensland, Queensland Brain Institute, Brisbane, QLD, Australia}

\affil[3]{Department of Genetics, University Medical Center Groningen, University of Groningen, Hanzeplein 1, Groningen, the Netherlands}

\affil[4]{Queensland Institute of Medical Research, Brisbane, Queensland, Australia}

\affil[5]{Estonian Genome Center, University of Tartu, Tartu, 51010, Estonia}

\affil[6]{School of Biology and Centre for Integrative Genomics, Georgia Institute of Technology, Atlanta, Georgia United States of America}

\affil[7]{Divisions of Endocrinology, Children's Hospital, Boston, MA, 02115, US}

\affil[8]{Medical and Population Genetics, Broad Institute, Cambridge, MA, 02142, US}

\affil[*]{Corresponding author: g.hemani@uq.edu.au}

}

@@

@@

Of the discovery interactions, 47 were \emph{cis}-\emph{cis} acting (both SNPs were on the same chromosome as the expression gene), 441 were \emph{cis}-\emph{trans}-acting, and 13 were \emph{trans}-\emph{trans}-acting. We observed a wide range of significant GP maps (Figure \ref{fig:gpmaps}) but the most common pattern of epistasis that we detected involved a \emph{trans}-SNP masking the effect of an additive \emph{cis}-SNP. For example, MBNL1 (involved in RNA modification and regulation of splicing \cite{Ho2004}) has a \emph{cis} effect at rs13069559 which in turn is controlled by 13 \emph{trans}-SNPs and one \emph{cis}-SNP that each exhibit a masking pattern, such that when the \emph{trans}-SNP is homozygous for the masking allele the decreasing allele of the \emph{cis}-SNP no longer has an effect (Supplementary Figure \ref{fig:MBNL1}. Each of these interactions have evidence for replication in at least one dataset and six are significant at the Bonferroni level (Supplementary Figure \ref{fig:circleplots}). We see similar epistatic networks involving multiple \emph{trans}-acting SNPs for other gene expresson levels too, for example TMEM149 (Supplementary Figure \ref{fig:TMEM149}), NAPRT1 (Supplementary Figure \ref{fig:NAPRT1}), TRAPPC5 (Supplementary Figure \ref{fig:TRAPPC5}), and CAST (Supplementary Figure \ref{fig:CAST}).

@@

We also demonstrate spacial organisation of interacting loci suggesting a mechanism by which biological function can lead to epistatic genetic variance. It has been shown that different chromosomal regions spatially colocalise in the cell through chromatin interactions \cite{Lieberman-Aiden2009}. We cross-referenced our epistatic SNPs with a map of chromosome interacting regions ($n = 96,139$) in K562 blood cell lines \cite{Lan2012} (Methods) and found that 44 epistatic interactions mapped to within 2Mb ($p < 1.8 \times 10^{-10}$), (Supplementary Figure \ref{fig:chromosomeinteractions}). Relatedly, there was significant enrichment of \emph{trans}-SNPs being located within 250bp to kid/KIF22 binding sites ($p = 8.4 \times 10^{-28}$) which are involved in intracellular chromosome transport \cite{Miki2001}. Interaction of distant loci may occur through physical proximity in transcriptional factories that organise across different chromosome regions and can regulate transcription of related genes \cite{Osborne2004, Rieder2013}.

@@

\begin{figure}
	\centering
	\includegraphics[width=5in]{circles_replication2}
	\caption{\textbf{Gene expression traits with four or more genetic interactions} Circle plots represent the genomic positions for SNPs (linking lines) and expression probes (red points). Chromosomes are represented by black blocks and ordered from 1 to 22 clockwise, starting from the top. Grey lines represent no evidence for replication, blue lines denote replication in at least one dataset, and red lines denote replication in two datasets. Most interactions are characterised as being \emph{cis}-\emph{trans} to the expression probe.}
	\label{fig:circleplots}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\includegraphics[width=5in]{OverlapAnnotation}
	\caption{\textbf{Location of SNPs relative to genomic features} All SNPs within 5kb and $r^2 > 0.8$ of each \emph{cis}- and \emph{trans}-SNP were taken to find which genomic regions were covered by the 501 significant interactions. There is enrichment for \emph{cis}-acting SNPs in promotor regions, and \emph{cis}- and \emph{trans}-acting SNPs in intronic regions.}
	\label{fig:snplocations}
\end{figure}
\clearpage

@@

\begin{figure}
	\centering
	\includegraphics[width=5in]{MBNL1}
	\caption{\textbf{Genotype-phenotype maps for 14 interactions controlling MBNL1} Each bar represents the mean phenotypic value for individuals in that genotype class. The rs13069559 SNP typically has a \emph{cis}-additive decreasing effect on the expression of MBNL1, but in many of these interactions the \emph{cis} effect is masked when the \emph{trans} SNP is homozygous.}
	\label{fig:mbnl13d}
\end{figure}
\clearpage

@@

>>>>

\documentclass{article}
\usepackage[superscript,biblabel]{cite}
\usepackage{graphicx}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage{authblk}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{lscape}

@@

\title{Detection and replication of epistasis influencing transcription in humans}
\date{}

\author[1,2,*]{Gibran Hemani}
\author[1,2]{Konstantin Shakhbazov}
\author[3]{Harm-Jan Westra}
\author[4]{Anjali K Henders}
\author[1,2]{Allan F. McRae}
\author[5]{Andres Metspalu}
\author[6]{Greg Gibson}
\author[4]{Nick G Martin}
\author[5,7,8]{Tonu Esko}
\author[3]{Lude Franke}
\author[4]{Grant W Montgomery}
\author[1,2]{Peter M Visscher}
\author[1,2]{Joseph E Powell}

\affil[1]{University of Queensland Diamantina Institute, University of Queensland, Princess Alexandra Hospital, Brisbane, Queensland, Australia}
\affil[2]{The University of Queensland, Queensland Brain Institute, Brisbane, QLD, Australia}
\affil[3]{Department of Genetics, University Medical Center Groningen, University of Groningen, Hanzeplein 1, Groningen, the Netherlands}
\affil[4]{Queensland Institute of Medical Research, Brisbane, Queensland, Australia}
\affil[5]{Estonian Genome Center, University of Tartu, Tartu, 51010, Estonia}
\affil[6]{School of Biology and Centre for Integrative Genomics, Georgia Institute of Technology, Atlanta, Georgia United States of America}
\affil[7]{Divisions of Endocrinology, Children's Hospital, Boston, MA, 02115, US}
\affil[8]{Medical and Population Genetics, Broad Institute, Cambridge, MA, 02142, US}
\affil[*]{Corresponding author: g.hemani@uq.edu.au}

@@

\clearpage

@@

Of the discovery interactions, 47 were \emph{cis}-\emph{cis} acting (both SNPs were on the same chromosome as the expression gene), 441 were \emph{cis}-\emph{trans}-acting, and 13 were \emph{trans}-\emph{trans}-acting. We observed a wide range of significant GP maps (Figure \ref{fig:gpmaps}) but the most common pattern of epistasis that we detected involved a \emph{trans}-SNP masking the effect of an additive \emph{cis}-SNP. For example, MBNL1 (involved in RNA modification and regulation of splicing \cite{Ho2004}) has a \emph{cis} effect at rs13069559 which in turn is controlled by 13 \emph{trans}-SNPs and one \emph{cis}-SNP that each exhibit a masking pattern, such that when the \emph{trans}-SNP is homozygous for the masking allele the decreasing allele of the \emph{cis}-SNP no longer has an effect (Supplementary Figure \ref{fig:MBNL1_3D}. Each of these interactions have evidence for replication in at least one dataset and six are significant at the Bonferroni level (Supplementary Figure \ref{fig:circleplots}). We see similar epistatic networks involving multiple \emph{trans}-acting SNPs for other gene expresson levels too, for example TMEM149 (Supplementary Figure \ref{fig:TMEM149_3D}), NAPRT1 (Supplementary Figure \ref{fig:NAPRT1_3D}), TRAPPC5 (Supplementary Figure \ref{fig:TRAPPC5_3D}), and CAST (Supplementary Figure \ref{fig:CAST_3D}).

@@

We also demonstrate spacial organisation of interacting loci suggesting a mechanism by which biological function can lead to epistatic genetic variance. It has been shown that different chromosomal regions spatially colocalise in the cell through chromatin interactions \cite{Lieberman-Aiden2009}. We cross-referenced our epistatic SNPs with a map of chromosome interacting regions ($n = 96,139$) in K562 blood cell lines \cite{Lan2012} (Methods) and found that 44 epistatic interactions mapped to within 2Mb ($p < 1.8 \times 10^{-10}$), (Supplementary Figure \ref{fig:chromosomeinteractions}). Interaction of distant loci may occur through physical proximity in transcriptional factories that organise across different chromosome regions and can regulate transcription of related genes \cite{Osborne2004, Rieder2012}.

@@

\begin{figure}
	\centering
	\includegraphics[width=5in]{circles_replication2}
	\caption{\textbf{Gene expression traits with four or more genetic interactions} Circle plots represent the genomic positions for SNPs (linking lines) and expression probes (red points). Chromosomes are represented by black blocks and ordered from 1 to 22 clockwise, starting from the top. Grey lines represent no evidence for replication, blue lines denote interactions that are outside the 97.5\% confidence interval or the Q-Q plot (Figure \ref{fig:qqMeta}), and red lines denote replication at the Bonferroni correction level. Most interactions are characterised as being \emph{cis}-\emph{trans} to the expression probe.}
	\label{fig:circleplots}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\includegraphics[width=5in]{OLapWithGenomicFeaturesFinal}
	\caption{\textbf{Location of SNPs relative to genomic features} All SNPs within 1kb and $r^2 > 0.8$ of each \emph{cis}- and \emph{trans}-SNP were taken to find which genomic features (\emph{x}-axis) were covered by the SNPs that compose the 501 significant interactions. Green bars represent the proportion (\emph{y}-axis) of the 528,509 SNPs used in the analysis that fall within the range of the different genomic features. There is enrichment for \emph{cis}-acting SNPs (red bars) in promotor regions, but \emph{trans}-acting SNPs (blue bars) are not enriched for genomic features.}
	\label{fig:snplocations}
\end{figure}
\clearpage

@@

\begin{figure}
	\centering
	\includegraphics[width=5in]{MBNL1_3D}
	\caption{\textbf{Genotype-phenotype maps for 14 interactions influencing the expression of MBNL1} Each bar represents the mean phenotypic value for individuals in that genotype class. The rs13069559 SNP typically has a \emph{cis}-additive decreasing effect on the expression of MBNL1, but in many of these interactions the \emph{cis} effect is masked when the \emph{trans} SNP is homozygous.}
	\label{fig:MBNL1_3D}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\includegraphics[width=5in]{TMEM149_3D}
	\caption{\textbf{Genotype-phenotype maps for 19 interactions influencing the expression of TMEM149} Each bar represents the mean phenotypic value for individuals in that genotype class. The rs13069559 SNP typically has a \emph{cis}-additive decreasing effect on the expression of TMEM149, but in many of these interactions the \emph{cis} effect is masked when the \emph{trans} SNP is homozygous.}
	\label{fig:TMEM149_3D}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\includegraphics[width=5in]{NAPRT1_3D}
	\caption{\textbf{Genotype-phenotype maps for 8 interactions influencing the expression of NAPRT1} Each bar represents the mean phenotypic value for individuals in that genotype class.}
	\label{fig:NAPRT1_3D}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\includegraphics[width=5in]{TRAPPC5_3D}
	\caption{\textbf{Genotype-phenotype maps for 16 interactions influencing the expression of TRAPPC5} Each bar represents the mean phenotypic value for individuals in that genotype class.}
	\label{fig:TRAPPC5_3D}
\end{figure}
\clearpage

\begin{figure}
	\centering
	\includegraphics[width=5in]{CAST_3D}
	\caption{\textbf{Genotype-phenotype maps for 15 interactions influencing the expression of CAST} Each bar represents the mean phenotypic value for individuals in that genotype class.}
	\label{fig:CAST_3D}
\end{figure}
\clearpage

@@

\clearpage
\section{Supplementary Tables}
\setcounter{table}{0}
\makeatletter 
\renewcommand{\thetable}{S\@arabic\c@table} 
\makeatletter

\begin{landscape}

\begin{ThreePartTable}
\begin{longtable}{|llr|lrrl|lrrl|rrrr|r|}

\caption{\textbf{Details on 501 interactions discovered in BSGS dataset}}\\

\hline
\multicolumn{3}{|c|}{Expression trait} & 
\multicolumn{4}{|c|}{SNP 1} & 
\multicolumn{4}{|c|}{SNP 2} & 
\multicolumn{4}{|c|}{Interaction statistic / $-\log_{10}p$-values} & \\
\hline
Gene ID\tnote{a} & 
Probe ID\tnote{b} & 
Chr. & 
rs ID & 
Chr. & 
Pos/Mb\tnote{c} & 
Association\tnote{d} & 
rs ID & 
Chr. & 
Pos/Mb\tnote{c} & 
Association\tnote{d} & 
BSGS\tnote{e} & 
Fehrmann\tnote{f} & 
EGCUT\tnote{f} & 
Meta\tnote{g} & 
Distance / Mb\tnote{h} \\
\hline
\endfirsthead

\multicolumn{16}{c}{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline
\multicolumn{3}{|c|}{Expression trait} & 
\multicolumn{4}{|c|}{SNP 1} & 
\multicolumn{4}{|c|}{SNP 2} & 
\multicolumn{4}{|c|}{Interaction statistic / $-\log_{10}p$-values} & \\
\hline
Gene ID\tnote{a} & 
Probe ID\tnote{b} & 
Chr. & 
rs ID & 
Chr. & 
Pos/Mb\tnote{c} & 
Association\tnote{d} & 
rs ID & 
Chr. & 
Pos/Mb\tnote{c} & 
Association\tnote{d} & 
BSGS\tnote{e} & 
Fehrmann\tnote{f} & 
EGCUT\tnote{f} & 
Meta\tnote{g} & 
Distance / Mb\tnote{h} \\
\hline
\endhead

\hline
\multicolumn{16}{r}{{Continued on next page}} \\
\endfoot

\hline \hline
\endlastfoot

ABCA7 & ILMN\_1743205 & 19 & rs3752237 & 19 & 1047161 & ABCA7 & rs596183 & 6 & 158100199 &  & 5.82 & 0.38 & 0.02 & 0.09 &  \\
  ABCA7 & ILMN\_1743205 & 19 & rs3752237 & 19 & 1047161 & ABCA7 & rs914737 & 9 & 139522101 &  & 5.50 &  &  &  &  \\
  ABCC3 & ILMN\_1677814 & 17 & rs9455 & 17 & 48771135 & ABCC3 & rs4732202 & 7 & 136057883 &  & 6.10 & 0.02 & 1.81 & 0.95 &  \\
  ACAT1 & ILMN\_1800008 & 11 & rs227064 & 11 & 108207393 & ACAT1 & rs4744894 & 9 & 72001517 &  & 6.59 & 1.04 & 1.78 & 2.02 &  \\
  ADCK1 & ILMN\_1698777 & 14 & rs12431896 & 14 & 78088813 & ADCK1 & rs4833241 & 4 & 122933691 &  & 5.59 & 0.36 & 1.14 & 0.87 &  \\
  ADCK1 & ILMN\_1698777 & 14 & rs8058066 & 16 & 88462550 &  & rs12431896 & 14 & 78088813 & ADCK1 & 6.58 & 2.04 & 0.83 & 2.05 &  \\
  ADK & ILMN\_2358626 & 10 & rs2395095 & 10 & 76446305 & ADK & rs10824092 & 10 & 75929517 &  & 6.69 & 18.33 & 21.21 & 39.82 & 0.517 \\
  AGAP6 & ILMN\_3239130 & 10 & rs2611512 & 10 & 51515534 & AGAP8 & rs2547996 & 5 & 95174319 &  & 6.22 &  &  &  &  \\
  AHSA2 & ILMN\_1798308 & 2 & rs10881585 & 9 & 137112421 &  & rs842647 & 2 & 61119471 &  & 7.15 & 1.83 & 1.93 & 2.88 &  \\
  AHSA2 & ILMN\_1798308 & 2 & rs2523971 & 6 & 29938258 & HLA-G & rs1177303 & 2 & 61388355 & AHSA2 & 5.45 & 0.92 & 0.64 & 0.94 &  \\
  AKTIP & ILMN\_1665982 & 16 & rs2896940 & 16 & 57721127 &  & rs13332406 & 16 & 53489705 & AKTIP & 6.91 & 0.16 & 0.99 & 0.57 & 4.231 \\
  AKTIP & ILMN\_1665982 & 16 & rs7189819 & 16 & 53536345 & AKTIP & rs1362032 & 7 & 125543391 &  & 5.93 & 0.71 & 0.20 & 0.42 &  \\
  AKTIP & ILMN\_1665982 & 16 & rs7189819 & 16 & 53536345 & AKTIP & rs1473017 & 4 & 179323762 &  & 6.18 & 0.27 & 0.30 & 0.23 &  \\
  ALDH3A2 & ILMN\_2401641 & 17 & rs3760489 & 17 & 19581009 & ALDH3A2 & rs11720112 & 3 & 161996349 &  & 6.26 & 0.33 & 1.37 & 1.01 &  \\
  ANG & ILMN\_1760727 & 14 & rs9322855 & 14 & 21153299 & ANG & rs4866516 & 5 & 3032625 &  & 5.75 & 0.02 & 0.20 & 0.04 &  \\
  ANPEP & ILMN\_1763837 & 15 & rs11073891 & 15 & 90363995 & ANPEP & rs3823523 & 7 & 154511163 &  & 5.85 & 0.44 & 1.09 & 0.90 &  \\
  ANPEP & ILMN\_1763837 & 15 & rs11073891 & 15 & 90363995 & ANPEP & rs6846031 & 4 & 178019148 &  & 6.31 & 0.47 & 0.17 & 0.26 &  \\
  AP3B1 & ILMN\_1768867 & 5 & rs6453374 & 5 & 77508159 & AP3B1 & rs4684443 & 3 & 4818792 &  & 5.94 & 0.05 &  &  &  \\
  APPL2 & ILMN\_1765076 & 12 & rs935251 & 12 & 105580918 & APPL2 & rs2769594 & 9 & 87918528 &  & 5.60 & 0.80 & 1.02 & 1.16 &  \\
  ARL17B & ILMN\_3231952 & 17 & rs12947580 & 17 & 75768225 &  & rs8079215 & 17 & 44064851 & ARL17B & 5.96 &  &  &  & 31.703 \\
  ARL17B & ILMN\_3231952 & 17 & rs2834541 & 21 & 35932619 &  & rs8079215 & 17 & 44064851 & ARL17B & 6.65 &  &  &  &  \\
  ARL17B & ILMN\_3231952 & 17 & rs8079215 & 17 & 44064851 & ARL17B & rs1950646 & 14 & 94722497 &  & 7.64 &  &  &  &  \\
  ARL17B & ILMN\_3231952 & 17 & rs8079215 & 17 & 44064851 & ARL17B & rs2197777 & 12 & 125831219 &  & 6.26 &  &  &  &  \\
  ARL17B & ILMN\_3231952 & 17 & rs8079215 & 17 & 44064851 & ARL17B & rs2684789 & 15 & 99492045 &  & 5.98 &  &  &  &  \\
  ARL17B & ILMN\_3231952 & 17 & rs8079215 & 17 & 44064851 & ARL17B & rs9834627 & 3 & 191203546 &  & 5.72 &  &  &  &  \\
  ATP13A1 & ILMN\_2134224 & 19 & rs4284750 & 19 & 19810050 &  & rs873870 & 19 & 19738554 &  & 5.30 & 12.18 & 3.25 & 14.23 & 0.071 \\
  BID & ILMN\_1763386 & 22 & rs8919 & 22 & 18213057 & BID & rs9804943 & 12 & 129906275 &  & 5.84 & 0.06 & 0.40 & 0.14 &  \\
  BID & ILMN\_2372413 & 22 & rs181405 & 22 & 18233000 &  & rs10888267 & 1 & 248059423 &  & 6.60 & 0.87 & 0.16 & 0.50 &  \\
  C11ORF17 & ILMN\_1752988 & 11 & rs2568061 & 11 & 8886260 & C11ORF17 & rs6553184 & 4 & 189150656 &  & 5.66 & 1.15 & 0.04 & 0.54 &  \\
  C13ORF18 & ILMN\_2196550 & 13 & rs2110603 & 16 & 6259852 &  & rs674754 & 13 & 46913416 & C13ORF18 & 6.66 & 0.28 & 0.28 & 0.22 &  \\
  C13ORF18 & ILMN\_2196550 & 13 & rs674754 & 13 & 46913416 & C13ORF18 & rs6857876 & 4 & 153610164 &  & 3.87 & 0.38 & 0.50 & 0.43 &  \\
  C14ORF173 & ILMN\_2393450 & 14 & rs11089825 & 22 & 37575398 &  & rs4983382 & 14 & 105189504 & C14ORF173 & 6.02 & 0.60 & 0.84 & 0.85 &  \\
  C14ORF173 & ILMN\_2393450 & 14 & rs3935344 & 15 & 92276674 &  & rs4983382 & 14 & 105189504 & C14ORF173 & 5.98 & 0.31 & 0.28 & 0.24 &  \\
  C14ORF173 & ILMN\_2393450 & 14 & rs4983382 & 14 & 105189504 & C14ORF173 & rs10754644 & 1 & 238724741 &  & 7.15 & 0.42 & 0.34 & 0.35 &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs1293455 & 18 & 13819673 &  & rs2655991 & 14 & 77574438 &  & 4.87 &  &  &  &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs2655991 & 14 & 77574438 &  & rs10972462 & 9 & 35427324 &  & 4.32 &  &  &  &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs2655991 & 14 & 77574438 &  & rs6445340 & 3 & 63371601 &  & 4.40 &  &  &  &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs2655991 & 14 & 77574438 &  & rs9787151 & 1 & 63179138 &  & 4.05 &  &  &  &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs4793445 & 17 & 70416307 &  & rs2655991 & 14 & 77574438 &  & 3.85 &  &  &  &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs6010061 & 22 & 51151724 &  & rs2655991 & 14 & 77574438 &  & 4.61 &  &  &  &  \\
  C14ORF4 & ILMN\_1804396 & 14 & rs7245800 & 19 & 52083552 &  & rs2655991 & 14 & 77574438 &  & 4.69 &  &  &  &  \\
  C17ORF60 & ILMN\_1747347 & 17 & rs9907897 & 17 & 63502633 &  & rs7405659 & 17 &  & C17ORF60 & 6.79 & 0.53 & 0.05 & 0.19 &  \\
  C1ORF86 & ILMN\_1726989 & 1 & rs2334323 & 6 & 110577257 &  & rs2257182 & 1 & 2082566 & C1ORF86 & 5.90 & 0.01 & 0.50 & 0.13 &  \\
  C1ORF86 & ILMN\_2097790 & 1 & rs2279474 & 18 & 46384412 &  & rs2460002 & 1 & 2119833 & C1ORF86 & 5.65 &  & 0.03 &  &  \\
  C1ORF86 & ILMN\_2097790 & 1 & rs7188668 & 16 & 25711358 &  & rs2460002 & 1 & 2119833 & C1ORF86 & 5.59 & 0.29 & 0.50 & 0.37 &  \\
  C21ORF57 & ILMN\_1795836 & 21 & rs4819271 & 21 & 48052838 &  & rs901964 & 12 & 48676038 & ZNF641 & 4.91 & 0.65 & 0.08 & 0.28 &  \\
  C21ORF57 & ILMN\_1795836 & 21 & rs9978658 & 21 & 48027084 &  & rs11701361 & 21 & 47764477 &  & 9.42 & 6.08 & 16.36 & 21.67 & 0.263 \\
  C5ORF4 & ILMN\_1728742 & 5 & rs1122762 & 18 & 45866512 &  & rs286595 & 5 & 154348552 & C5ORF4 & 5.55 & 0.72 & 0.04 & 0.27 &  \\
  C8ORF59 & ILMN\_1653205 & 8 & rs12429804 & 13 & 36577930 &  & rs2896452 & 8 & 86102223 & C8ORF59 & 5.49 & 0.29 & 0.02 & 0.07 &  \\
  C8ORF59 & ILMN\_1653205 & 8 & rs12454561 & 18 & 31272238 &  & rs2896452 & 8 & 86102223 & C8ORF59 & 5.45 & 0.31 &  &  &  \\
  C8ORF59 & ILMN\_1653205 & 8 & rs2896452 & 8 & 86102223 & C8ORF59 & rs1004564 & 4 & 55242625 &  & 7.62 & 0.38 & 0.18 & 0.21 &  \\
  C8ORF59 & ILMN\_1653205 & 8 & rs7152284 & 14 & 52273663 &  & rs2896452 & 8 & 86102223 & C8ORF59 & 5.67 & 2.18 & 0.07 & 1.33 &  \\
  C8ORF59 & ILMN\_1653205 & 8 & rs8051751 & 16 & 7188323 &  & rs2896452 & 8 & 86102223 & C8ORF59 & 5.79 & 1.39 & 0.18 & 0.87 &  \\
  C9ORF72 & ILMN\_1741881 & 9 & rs10122902 & 9 & 27556780 & C9ORF72 & rs2526698 & 1 & 242029101 &  & 6.36 & 0.96 & 0.01 & 0.37 &  \\
  CABC1 & ILMN\_1731064 & 1 & rs12765847 & 10 & 4353908 &  & rs3738725 & 1 & 227174210 & CABC1 & 6.36 & 0.94 & 0.00 & 0.34 &  \\
  CARD9 & ILMN\_1712532 & 9 & rs4266763 & 9 & 139289825 & INPP5E & rs684040 & 1 & 82128660 &  & 5.81 &  &  &  &  \\
  CARD9 & ILMN\_1712532 & 9 & rs4573661 & 11 & 6026661 &  & rs4077515 & 9 & 139266496 & INPP5E & 6.61 & 0.09 & 0.86 & 0.42 &  \\
  CAST & ILMN\_1717234 & 5 & rs1157079 & 20 & 6778978 &  & rs7733671 & 5 & 96000269 & CAST & 7.07 & 0.23 & 0.96 & 0.62 &  \\
  CAST & ILMN\_1717234 & 5 & rs12463169 & 19 & 17321669 &  & rs7733671 & 5 & 96000269 & CAST & 5.73 & 0.02 & 2.85 & 1.75 &  \\
  CAST & ILMN\_1717234 & 5 & rs12599264 & 16 & 81840122 &  & rs7733671 & 5 & 96000269 & CAST & 7.00 &  &  &  &  \\
  CAST & ILMN\_1717234 & 5 & rs12719343 & 5 & 125369113 &  & rs7733671 & 5 & 96000269 & CAST & 7.68 & 0.36 & 1.57 & 1.20 & 29.369 \\
  CAST & ILMN\_1717234 & 5 & rs1410575 & 9 & 78255630 &  & rs7733671 & 5 & 96000269 & CAST & 6.55 & 0.13 & 1.34 & 0.78 &  \\
  CAST & ILMN\_1717234 & 5 & rs166444 & 8 & 78392770 &  & rs7733671 & 5 & 96000269 & CAST & 7.01 & 0.27 & 0.52 & 0.37 &  \\
  CAST & ILMN\_1717234 & 5 & rs17648036 & 15 & 27311111 &  & rs7733671 & 5 & 96000269 & CAST & 7.81 & 0.97 & 0.03 & 0.41 &  \\
  CAST & ILMN\_1717234 & 5 & rs17818702 & 11 & 86107920 &  & rs7733671 & 5 & 96000269 & CAST & 6.62 & 1.15 & 0.59 & 1.09 &  \\
  CAST & ILMN\_1717234 & 5 & rs227402 & 14 & 70496867 &  & rs7733671 & 5 & 96000269 & CAST & 6.12 & 0.11 & 0.01 & 0.01 &  \\
  CAST & ILMN\_1717234 & 5 & rs2822124 & 21 & 15166804 &  & rs7733671 & 5 & 96000269 & CAST & 6.87 &  &  &  &  \\
  CAST & ILMN\_1717234 & 5 & rs3757155 & 6 & 136458593 &  & rs7733671 & 5 & 96000269 & CAST & 7.24 & 0.07 & 0.33 & 0.12 &  \\
  CAST & ILMN\_1717234 & 5 & rs4503014 & 7 & 31149140 &  & rs7733671 & 5 & 96000269 & CAST & 5.88 & 0.92 & 1.56 & 1.72 &  \\
  CAST & ILMN\_1717234 & 5 & rs7474890 & 10 & 59590078 &  & rs7733671 & 5 & 96000269 & CAST & 6.74 & 0.49 & 0.12 & 0.23 &  \\
  CAST & ILMN\_1717234 & 5 & rs7733671 & 5 & 96000269 & CAST & rs10802643 & 1 & 238120177 &  & 7.42 & 0.75 & 0.78 & 0.93 &  \\
  CAST & ILMN\_1717234 & 5 & rs7733671 & 5 & 96000269 & CAST & rs12650909 & 4 & 170192890 &  & 7.42 & 0.23 & 0.78 & 0.50 &  \\
  CAST & ILMN\_1717234 & 5 & rs7733671 & 5 & 96000269 & CAST & rs2203733 & 2 & 224093101 &  & 6.07 & 0.22 & 0.87 & 0.54 &  \\
  CAST & ILMN\_1717234 & 5 & rs7733671 & 5 & 96000269 & CAST & rs2641772 & 3 & 195531841 &  & 6.93 & 0.19 & 0.26 & 0.15 &  \\
  CAT & ILMN\_1651705 & 11 & rs872311 & 18 & 66175386 &  & rs11032695 & 11 & 34447586 & CAT & 6.41 & 0.26 & 0.30 & 0.22 &  \\
  CCDC88B & ILMN\_1772208 & 11 & rs2353203 & 19 & 17099980 &  & rs541207 & 11 & 64125142 & CCDC88B & 5.68 & 0.33 & 0.37 & 0.31 &  \\
  CCDC88B & ILMN\_1772208 & 11 & rs694739 & 11 & 64097233 & CCDC88B & rs12771349 & 10 & 96998193 &  & 5.62 & 0.23 & 0.18 & 0.14 &  \\
  CD36 & ILMN\_1784863 & 7 & rs3211834 & 7 & 80280117 &  & rs1254900 & 2 & 85816334 & VAMP8 & 6.93 & 0.15 & 0.01 & 0.02 &  \\
  CD55 & ILMN\_1800540 & 1 & rs750801 & 11 & 76033374 &  & rs6700168 & 1 & 207502534 & CD55 & 5.09 & 0.08 & 0.03 & 0.02 &  \\
  CD93 & ILMN\_1704730 & 20 & rs1884655 & 20 & 23074375 & CD93 & rs10255470 & 7 & 157182040 &  & 6.06 & 1.74 & 0.24 & 1.20 &  \\
  CD93 & ILMN\_1704730 & 20 & rs1884655 & 20 & 23074375 & CD93 & rs4696726 & 4 & 7992632 &  & 5.71 & 0.13 & 0.80 & 0.42 &  \\
  CD93 & ILMN\_1704730 & 20 & rs1884655 & 20 & 23074375 & CD93 & rs7622580 & 3 & 196721395 &  & 5.56 & 0.04 & 0.27 & 0.08 &  \\
  CD93 & ILMN\_1704730 & 20 & rs1884655 & 20 & 23074375 & CD93 & rs838875 & 12 & 125145394 &  & 6.31 & 0.24 & 1.67 & 1.16 &  \\
  CD93 & ILMN\_1704730 & 20 & rs1884655 & 20 & 23074375 & CD93 & rs9576388 & 13 & 38434472 &  & 7.88 & 0.71 & 0.22 & 0.45 &  \\
  CD93 & ILMN\_1704730 & 20 & rs2868504 & 20 & 37771578 &  & rs1884655 & 20 & 23074375 & CD93 & 5.71 & 0.64 & 0.75 & 0.81 & 14.697 \\
  CD93 & ILMN\_1704730 & 20 & rs4813479 & 20 & 23076914 & CD93 & rs10925747 & 1 & 238899903 &  & 7.43 &  &  &  &  \\
  CD93 & ILMN\_1704730 & 20 & rs4813479 & 20 & 23076914 & CD93 & rs2873420 & 8 & 136500554 &  & 7.02 &  &  &  &  \\
  CD93 & ILMN\_1704730 & 20 & rs4813479 & 20 & 23076914 & CD93 & rs4328531 & 18 & 74439542 &  & 6.13 &  &  &  &  \\
  CD93 & ILMN\_1704730 & 20 & rs4813479 & 20 & 23076914 & CD93 & rs4789981 & 17 & 77264482 &  & 6.08 &  &  &  &  \\
  CDC16 & ILMN\_2339796 & 13 & rs861544 & 14 & 104162263 &  & rs7324744 & 13 & 115008038 & CDC16 & 5.46 & 0.21 & 0.14 & 0.11 &  \\
  CDK5R1 & ILMN\_1730928 & 17 & rs9905940 & 17 & 46614102 & HOXB2 & rs11655031 & 17 & 30833162 & CDK5R1 & 5.47 & 0.95 & 0.07 & 0.45 & 15.781 \\
  CEACAM21 & ILMN\_1745949 & 19 & rs200609 & 20 & 51956250 &  & rs4803481 & 19 & 42066556 & CEACAM21 & 6.15 & 0.90 & 0.12 & 0.48 &  \\
  CEACAM21 & ILMN\_1745949 & 19 & rs4803481 & 19 & 42066556 & CEACAM21 & rs2421050 & 5 & 158943044 &  & 6.67 & 2.16 & 0.16 & 1.44 &  \\
  CEP192 & ILMN\_1703754 & 18 & rs6505780 & 18 & 13069782 & CEP192 & rs13132719 & 4 & 180265266 &  & 5.75 & 0.15 & 0.24 & 0.12 &  \\
  CEP63 & ILMN\_1787808 & 3 & rs3825569 & 14 & 101350298 &  & rs13079012 & 3 & 134247706 & ANAPC13 & 6.36 & 0.23 & 0.10 & 0.09 &  \\
  CES1 & ILMN\_2359945 & 16 & rs8192935 & 16 & 55861794 & CES1 & rs772788 & 2 & 235248562 &  & 5.65 &  &  &  &  \\
